Figures to insert in text

### 2018-03-09 Chapters/Chapter02.tex
SDM minor changes

Performance is an important part of our framework. Running an SDM memory consumes a lot of resource from both CPU and RAM.

For instance, each scan in 1,000,000 hard-locations with 1,000 bits executes $10^9$ bit compares through $10^9/64 = 15,625,000$ XORs and calls to the built-in popcount. So, 10,000 writes execute $10^{13}$ bit compares, while a 6-iterative reading executes $6 \cdot 10^{12}$ bit compares. The heatmap of Figure \ref{fig:cir-dist-10k-writes-kanerva} executed $3.05 \cdot 10^{15}$ bit compares. For comparison, the number of seconds since Jesus's birth is 63,639,648,000 = $6.36 \cdot 10^{10}$. The number of people who have ever lived on earth is estimated to be $1,08 \cdot 10^{11}$. There are approximtely $1.8 \cdot 10^{9}$ websites in the internet.

Amazon EC2 p3.2xlarge has generated the heatmap of Figure \ref{fig:cir-dist-10k-writes-kanerva} in 15 minutes and 3 seconds. It has compared $3.37 \cdot 10^{12}$ bits per second through $52.6 \cdot 10^{9} = 52.6 \text{ billion}$ XORs and popcounts per second.

@@

@@

It is no coincidence that scientific journals such as BMC Neuroscience, or the Journal of Machine Learning Research have specific sections on open-source software. The journal Neurocomputing even goes as far as to state that “software is scientific method by machine”.

>>>>

Performance matters --- and has always mattered. If an experiment takes a few seconds, there is no point arguing whether we should try it. If it takes a few hours, maybe we should think first. If it takes a few days, it is more important to make a good plan. As SDM consumes a lot of both processor and memory resources, some experiments may take a long time.

Each scan a 1,000-bits SDM with 1,000,000 hard-locations executes $10^9$ bit compares through $10^9/64 = 15,625,000$ XORs and calls to the built-in popcount. So, 10,000 writes execute $10^{13}$ bit compares, while a 6-iterative reading executes $6 \cdot 10^{12}$ bit compares. The heatmap of Figure \ref{fig:cir-dist-10k-writes-kanerva} executed $3.05 \cdot 10^{15}$ bit compares. For comparison, the number of seconds since Jesus's birth is 63,639,648,000 = $6.36 \cdot 10^{10}$. The number of people who have ever lived on earth is estimated to be $1,08 \cdot 10^{11}$. There are approximtely $1.8 \cdot 10^{9}$ websites in the internet. A modern laptop can increment a counter $5 \cdot 10^{8}$ times per second. Hence, a naive implementation of SDM may take several hours to simply write 10,000 random bitstrings.

Amazon EC2 p3.2xlarge has generated the heatmap of Figure \ref{fig:cir-dist-10k-writes-kanerva} in 15 minutes and 3 seconds. It has compared $3.37 \cdot 10^{12}$ bits per second through $52.6 \cdot 10^{9} = 52.6 \text{ billion}$ XORs and popcounts per second. It is a great improvement when compared to the first versions of the code which took 16 hours to generate the same heatmap (and its memory use was already optimized and the computations were distributed in threads).

@@

MacBook 1000 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	1000	23.6049609184	42.363976092	23.6049609184
single_scan1	1000	13.2222340107	75.6301846716	13.2222340107
single_scan2	1000	47.2828419209	21.1493209667	47.2828419209
single_scan3	1000	33.0640568733	30.2443225231	33.0640568733
single_scan4	1000	40.3230810165	24.7996922554	40.3230810165
single_scan5	1000	31.5100109577	31.7359458028	31.5100109577
single_scan5_unroll	1000	27.5569870472	36.288437422	27.5569870472
single_scan6	1000	39.4823219776	25.3277910192	39.4823219776

MacBook 256 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	1000	8.36867690086	119.493202073	8.36867690086
single_scan1	1000	10.4354770184	95.8269562801	10.4354770184
single_scan2	1000	23.4823930264	42.5850976465	23.4823930264
single_scan3	1000	25.5149869919	39.1926517665	25.5149869919
single_scan4	1000	42.3955621719	23.5873744508	42.3955621719
single_scan5	1000	24.4205920696	40.9490481291	24.4205920696
single_scan5_unroll	1000	22.7717738152	43.9140142581	22.7717738152
single_scan6	1000	42.1847259998	23.7052624214	42.1847259998

EC2 p3.2xlarge 1000 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	3000	2.09311103821	1433.27322117	0.697703679403
single_scan1	3000	1.64607286453	1822.51956438	0.548690954844
single_scan2	3000	2.57495617867	1165.06837082	0.858318726222
single_scan3	3000	3.06142997742	979.934220978	1.02047665914
single_scan4	3000	3.30994796753	906.358658635	1.10331598918
single_scan5	3000	2.8592748642	1049.21707163	0.953091621399
single_scan6	3000	3.12985897064	958.509641533	1.04328632355

EC2 p3.2xlarge 256 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	3000	1.09906792641	2729.58561334	0.366355975469
single_scan1	3000	1.10967302322	2703.49908236	0.369891007741
single_scan2	3000	2.21544480324	1354.12987749	0.738481601079
single_scan3	3000	1.9066619873	1573.43043496	0.635553995768
single_scan4	3000	3.15382003784	951.227389009	1.05127334595
single_scan5	3000	1.87652993202	1598.69552241	0.625509977341
single_scan6	3000	3.04240322113	986.062589983	1.01413440704

EC2 p3.2xlarge 10k bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	500	10.3001351357	48.5430524372	20.6002702713
single_scan1	500	2.47107696533	202.340925441	4.94215393066
single_scan2	500	2.5089058876	199.290058057	5.01781177521
single_scan3	500	3.0364408493	164.666471311	6.07288169861
single_scan4	500	2.99925804138	166.707896787	5.99851608276
single_scan5	500	2.68434309959	186.265310152	5.36868619919
single_scan6	500	2.98077511787	167.741604189	5.96155023575

EC2 p2.xlarge 1000 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	3000	11.3801429272	263.617075743	3.79338097572
single_scan1	3000	11.8365280628	253.452700325	3.94550935427
single_scan2	3000	25.6270592213	117.063763505	8.54235307376
single_scan3	3000	29.2102689743	102.70360751	9.73675632477
single_scan4	3000	34.1599340439	87.8221836186	11.3866446813
single_scan5	3000	29.8609650135	100.465607814	9.9536550045
single_scan6	3000	34.0075969696	88.2155832028	11.3358656565

EC2 p2.xlarge 256 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	3000	2.28510403633	1312.85051022	0.761701345444
single_scan1	3000	2.42481589317	1237.20733126	0.808271964391
single_scan2	3000	16.7731001377	178.857812531	5.59103337924
single_scan3	3000	18.9349951744	158.436797705	6.31166505814
single_scan4	3000	30.8822939396	97.1430427373	10.2940979799
single_scan5	3000	20.0731289387	149.453531094	6.69104297956
single_scan6	3000	30.8959820271	97.1000046988	10.2986606757

EC2 p2.xlarge 10k bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	500	17.7273669243	28.204978333	35.4547338486
single_scan1	500	28.9013559818	17.3002263394	57.8027119637
single_scan2	500	31.8554549217	15.6958989042	63.7109098434
single_scan3	500	19.9614479542	25.0482831279	39.9228959084
single_scan4	500	22.749904871	21.9781138794	45.499809742
single_scan5	500	21.7587711811	22.9792388476	43.5175423622
single_scan6	500	20.7129361629	24.1395037414	41.4258723259

@@

It is no coincidence that scientific journals such as BMC Neuroscience, or the Journal of Machine Learning Research have specific sections on open-source software. The journal Neurocomputing states, bluntly: “software is scientific method by machine”.

### 2018-03-09 Chapters/sdm-applications.tex
SDM minor changes

\chapter{Results (vi): Supervised image noise filtering application}

@@

>>>>

\chapter{Results (vi): Image noise filtering application}

@@

In the learning phase, 200 noisy images were generated and written into SDM. Half of the letter ``I'' and half of the letter ``T'' (see Figure \ref{fig:filter-training}). They were written in their own addresses, i.e., write(address=bs\_image, datum=bs\_image).

\begin{figure}[!htb]
  \subfloat[Letter ``I'' with 15\% of noise. ]{\includegraphics[width=\textwidth]{./images02/filter/training-i.png}}

  \subfloat[Letter ``T'' with 15\% of noise. ]{\includegraphics[width=\textwidth]{./images02/filter/training-t.png}}

  \caption{Training images written into the SDM. They were written in their own addresses --- write(address=bs\_image, datum=bs\_image).}
  \label{fig:filter-training}
\end{figure}
